Paper 4

### 2024-08-22 Rmd/Paper4.Rmd
Fixed error with mean being calculated from the whole dataset, while the model was estimated only using the pre-post values. (for prototype 2)

#library(ppcor) # partiell correlation
#library(mice) # missing
```

@@

@@

# only 13 from both pre-post
prot2_within_between_13 <- lme(TPACK ~ TK_S + TK_mean + PCK_S + PCK_mean + factor(datasett), 
                   random=~1|Subject, method="REML", 
                   data=data_emne2_v23[alle_studenter_v23 & !data_emne2_v23$datasett == "pre2",])

@@

```{r prot2_vc}
# does not converge with only 13 respondents
prot2_var_coeff <- lme(TPACK ~ TK_S + TK_mean + PCK_S + PCK_mean + factor(datasett), 
                   random=~TK_S|Subject, method="ML", data=data_emne2_v23[ !data_emne2_v23$datasett == "pre2",]) # alle_studenter_v23 &
```

@@

```{r}
library(MuMIn) # AICc
AICc(prot1_within_between, prot1_var_coeff, REML=F)
AICc(prot2_within_between, prot2_var_coeff, REML=F)
```

@@

prot2_within_between_13_REML <- lme(TPACK ~ TK_S + TK_mean + PCK_S + PCK_mean + factor(datasett), 
                   random=~1|Subject, method="REML", 
                   data=data_emne2_v23[alle_studenter_v23 & !data_emne2_v23$datasett == "pre2",])

>>>>

#library(ppcor) # partiell correlation
#library(mice) # missing
library(MuMIn) # AICc

@@

```{r prot2_centering_prepost}
# do not include pre2-data
data_emne2_v23_pp <- data_emne2_v23[!data_emne2_v23$datasett == "pre2",]

alle_studenter_v23_pp <-
  alle_studenter_v23[!data_emne2_v23$datasett == "pre2"]

# TK
# calculate mean for each subject / id; ref.: https://stackoverflow.com/a/34502529
data_emne2_v23_pp$TK_mean <- with(data_emne2_v23_pp, ave(x = TK, Subject, FUN = mean))
data_emne2_v23_pp$TK_S <- data_emne2_v23_pp$TK - data_emne2_v23_pp$TK_mean

# PCK interval
data_emne2_v23_pp$PCK_mean <- with(data_emne2_v23_pp, ave(x = PCK, Subject, FUN = mean))
data_emne2_v23_pp$PCK_S <- data_emne2_v23_pp$PCK - data_emne2_v23_pp$PCK_mean

# TPACK
data_emne2_v23_pp$TPACK_mean <- with(data_emne2_v23_pp, ave(x = TPACK, Subject, FUN = mean))
data_emne2_v23_pp$TPACK_S <- data_emne2_v23_pp$TPACK - data_emne2_v23_pp$TPACK_mean
```

@@

# only 13 from both pre-post
prot2_within_between_13 <- lme(TPACK ~ TK_S + TK_mean + PCK_S + PCK_mean + factor(datasett), 
                   random=~1|Subject, method="REML", 
                   data=data_emne2_v23_pp[alle_studenter_v23_pp,])

@@

using data_emne2_v23[ !data_emne2_v23$datasett == "pre2",] gives an error in the estimate, since TK_mean, etc. are calculated using the mean for all three datapoints, not only pre1 and post. It does not converge if I use the _pp dataset.

```{r prot2_vc}
# does not converge with only 13 respondents
prot2_var_coeff <- lme(TPACK ~ TK_S + TK_mean + PCK_S + PCK_mean + factor(datasett), 
                   random=~TK_S|Subject, method="ML", data=data_emne2_v23[ !data_emne2_v23$datasett == "pre2",]) # 
```

@@

```{r}
AICc(prot1_within_between, prot1_var_coeff, REML=F)
AICc(prot2_within_between, prot2_var_coeff, REML=F)
```

@@

prot2_within_between_13_REML <- lme(TPACK ~ TK_S + TK_mean + PCK_S + PCK_mean + factor(datasett), 
                   random=~1|Subject, method="REML", 
                   data=data_emne2_v23_pp[alle_studenter_v23_pp,])
